SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-08 scipy-1.0/subpackages.tex
Mentioned tutorials again per reviewer comment

Here we summarize the scope and capabilities of each subpackage.

@@

    The name comes the class of functions traditionally known as ``special

@@

    such as Airy, Bessel, etc.; orthogonal families of polynomials;

>>>>

Here we summarize the scope and capabilities of each subpackage.
Additional information is available in the SciPy Tutorial\cite{SciPy_tutorials} and
API Reference\cite{SciPy_API}.

@@

    The name comes from the class of functions traditionally known as ``special

@@

    such as Airy, Bessel, etc.; families of orthogonal polynomials;
